\documentclass[12pt,oneside]{gsbook}
\usepackage{greensocs}

\usepackage{ulem} % allow strikeout/strikethrough text with \sout{}

%\usepackage{array}
%\usepackage{xspace}
%\usepackage{fancyvrb}

%%% To make it work with Drupal:
%%% 1) Delete this package listings references below
\usepackage{listings}
\lstset{
  language=C++,
  breaklines=true,
  captionpos=b
  aboveskip=15pt,
  basicstyle=\ttfamily \small,
  stepnumber=5,
  numbersep=5pt,
  frame=trbl
}
%%% 2) replace text: ``lstlisting'' with ``verbatim''
%%% 3) remove line that begins with \lstset


\def\example#1{\begin{center}\colorbox{lightgrey}{\begin{tabular}{|p{0.6\paperwidth}|}\hline\\#1\\ \\ \hline\end{tabular}}\end{center}}

\newsavebox{\examplebox}
\newenvironment{exampleenv}{\begin{lrbox}{\examplebox}\begin{minipage}{0.6\paperwidth}}{\end{minipage}\end{lrbox}\example{\usebox{\examplebox}}}
\newcommand{\tick}{$\sqrt{}$}

\author{Copyright GreenSocs Ltd 2008}
\title{GreenMessage User Manual}

\begin{document}
\maketitle
\tableofcontents



\chapter{Introduction}
\label{INTRO}

GreenMessage is a framework to pass messages from one SystemC module
to another.

This project offers a simple API to support assembling a data
structure, a so-called message, and send this message to some other module
in the system that implements a receiver interface for messages.

The message contents are based on properties that map names to
values. The map of names supports hierarchy. By convention, the
hierarchy separator is the dot `.´ character. A valid name for a
property is for example the string \texttt{my\_cpu.cache.size}. The values for
each property are stored in a type-independent way, and can be
retrieved as an integral or real number, a boolean, or as a string.

The module that will receive the message is located by name look-up,
and a \texttt{write} or \texttt{nb\_write} method is invoked to send the message to its
destination. The receiver module implementation can chose get the
message delivered to a fifo or it can handle the message directly.  The
interface is in fact SystemC's \texttt{sc\_fifo\_out\_if<>} with the
GreenMessage message type as the template's parameter.

The motivation for GreenMessage is to provide a low-level interface
which can be used as a transport mechanism for user-defined protocols.
GreenMessage is characterised by
\begin{itemize}
\item Interpreted data type with arbitrary payload capability meaning
re-compilation is not always necessary on protocol change.
\item Name lookup rather than binding, allowing dynamic and cross-hierarchical
communications.
\end{itemize}
GreenMessage is particularly suited to communications between languages,
for example between SystemC and an embedded dynamically-typed language
like Python or Lua.


\chapter{Usage}
\label{USAGE}

All the functionality is defined in the header
\texttt{<greenmessage/greenmessage.hpp>}. After including this file, some
names get defined in the namespace \texttt{gs}::\texttt{msg}. They are listed
below:


\section{Class Message}

A message is a mapping of name-$>$value. In fact, this class is
inherited from std::map, and can use the methods provided by this
parent to retrieve the values or to iterate over the first level of
property names. Both key and value accepts numbers and
strings. Examples:

\begin{lstlisting}
gs::msg::Message msg;
msg["command"] = "start";
msg["repeat"] = 10;
msg[1] = "test";
msg[2] = 42.123;
\end{lstlisting}

The mapping is hierarchical and implemented as a tree. The hierarchy
can be accessed in two ways: (1) using a dot '.' in the name string or
(2) use the subscript operator multiple times.

\begin{lstlisting}
msg["my_cpu.cache"]["size"] = 4096
msg["my_cpu"]["cache.type"] = "wb";
\end{lstlisting}

Getting a reference to a branch is a low-cost operation:

\begin{lstlisting}
gs::msg::Message& my_cache = msg["my_cpu"]["cache"];
cout << my_cache["size"];   // outputs 4096 that was set above
\end{lstlisting}

When using methods of the base class, the user's code normally
needs to indicate to the compiler that this is what is wanted.  The
base class name is \texttt{children\_map} so the code might look
like this:

\begin{lstlisting}
for(Message::children_map::iterator
    ix = my_message.begin(); ix != my_message.end(); ix++)
{
      cout << ix->first << " = " << ix->second << endl;
}
\end{lstlisting}

A message object is always in one of two states.  It is either
a mapping or a value.  Values are the bottom level of the hierarchy.
For example in the first message constructed in this section,
\texttt{msg} is a map, but \texttt{msg["command"]} is a value.  In the
second example listing, \texttt{msg}, \texttt{msg["my\_cpu"]} and
\texttt{msg["my\_cpu.cache"]} are maps, but \texttt{msg["my\_cpu.cache.size"]}
and \texttt{msg["my\_cpu.cache.type"]} are values.

The state of a message changes when something is assigned to it or
an element of its map is created.  Note that accessing a non-existent
element of the map will cause the element to be created (unless the
message is constant) and hence will force the state to be a mapping.

Messages whose state is value can be automatically cast
to most types of variable.  Integers, floating points and strings all
work.  For example:

\begin{lstlisting}
gs::msg::Message msg;
msg["pi"] = "3.14";
msg["e"] = 2.71;
msg["zero"] = 0;
int z = msg["zero"];
std::string e = msg["e"];
float p = msg["pi"];
\end{lstlisting}

The GreenMessage interface passes messages by const reference.  The receiver
may make a copy of a message, in which case the copy is not constant and
may be modified.  This copy can be done by simple assignment.  If a
message FIFO is used (see below) such a copy happens automatically.
However if user code implements the WriteIf interface directly and
does not take a copy of incoming messages, it will need to work with
constant messages.  There are a few differences between constant and
non-constant messages:
\begin{itemize}
\item The operator $[key]$ used to access elements of a message returns
a const reference for a const message, so as expected the message
content can not be changed.
\item The operator $[key]$ creates a new element of a non-const
message if the key is missing.  But for a const message if the key is
missing a C++ exception is thrown.
\item Iteration over a const message must use a
\texttt{gs::msg::Message::children\_map::const\_iterator} not a normal
iterator.
\item The \texttt{find()} method is defined differently for const
messages.
\end{itemize}

\subsection{Class Methods}
\begin{itemize}
\item\texttt{bool has\_value() const} returns \texttt{true} for a value
and \texttt{false} for a mapping.
\item\texttt{gs::Message *find(const key\_type \&k)} where the parameter \texttt{k}
can be of any type supported as a key, returns 0 if the message is a
value or if the key is not in the mapping.  Returns a pointer to the sub-message
with that key, if the key is in the message.
\item\texttt{bool find(const key\_type \&k) const} where the parameter \texttt{k}
can be of any type supported as a key, returns false if the message is a
value or if the key is not in the mapping.  Returns true otherwise.  This
method is, unlike the other find(), useable for const Messages.
\item\texttt{void erase(const key\_type \&k)} where the parameter \texttt{k}
can be of any type supported as a key, will search for a sub-message with that
key and remove it if one is found.
\item\texttt{size\_t max\_numerical\_key() const} returns the largest value that can
be obtained by casting the message's keys to integers.  Defaults to 0.
\item\texttt{unsigned length\_as\_array() const} tests to see if the message
contains only the non-negative integers [0, 1, 2, ... $n-1$) as keys.  If this is
true, $n$ is returned.  Otherwise 0 is returned.  This permits a message
to be used as an array length $n$ of messages.
\end{itemize}

\section{Class WriteIf}

This interface contains the method write(Message). The implementation
depends on the module that receives the message. One option is to send
the message to a sc\_fifo$<$Message$>$, other option is to implement this
interface directly in the sc\_module.

The interface is the \texttt{sc\_fifo\_out\_if}, which contains four methods:
\begin{itemize}
\item\texttt{void write(const gs::msg::Message \&m)}
\item\texttt{bool nb\_write(const gs::msg::Message \&m)}
\item\texttt{int num\_free() const}
\item\texttt{const sc\_event \&data\_read\_event() const}
\end{itemize}

\section{Class WriteIfGroup}

This is a group of WriteIf. The group of receivers can be modified
with the methods \texttt{insert(WriteIf)} and \texttt{erase(WriteIf)}. It is itself a
WriteIf, and the method \texttt{write(Message)} is delivered to all the
registered receivers.  The method \texttt{num\_free()} returns the smallest \texttt{num\_free()}
of any member of the group.  The method \texttt{nb\_write()} will return false unless
\texttt{num\_free()} is greater than 0 for all members of the group, and not deliver
the message to any member in this case.  The member \texttt{data\_read\_event()} returns
the \texttt{data\_read\_event()} of the group member with the smallest \texttt{num\_free()}.
This should allow WriteIfGroups to be nested in most cases.

\section{Function broadcast()}

This function finds all the existing receivers and returns a WriteIf
that is in fact a WriteIfGroup.  This group can be copied and
modified, allowing a selection like ``all minus some''.


\section{Function findReceiver(string)}

This function does a look-up in the GreenMessage name registry to find
an object with the given name that can receive messages. This object
can be anything that implements the WriteIf interface. A reference
to the WriteIf is returned, so
the write method of this interface can be used to send several
messages to the named receiver.


\section{Class receiver\_base}

A receiver module can inherit from this class to register itself in
the GreenMessage name registry and thus make itself available to the
function \texttt{findReceiver}.
 The registration is done in construction time and doesn't
change during simulation.  The constructor has a single required argument,
the {\em full} name of the endpoint.

The class contains a static method \texttt{print\_registry} which may be
useful for debugging problems with finding endpoints.

\section{Class receiver\_proxy}

For cases where an endpoint already exists and the user needs to make it
visible in the GreenMessage hierarchy under a different name, an object of
the class \texttt{receiver\_proxy} can be used.

The constructor takes two arguments, a reference to the existing endpoint (any
object derived from WriteIf) and the full name to be used in the GreenMessage
registry.  The name may be provided either as a string or a char array.

The class has a method \texttt{std::string registered\_name()} which gives the
name used in the GreenMessage registry.

\section{Class MessageFifo}

A class derived from \texttt{sc\_fifo<Message>}.  Basically it is a normal
SystemC FIFO that registers itself as an endpoint in the GreenMessage registry.
It has the same methods and constructors as an \texttt{sc\_fifo<Message>} with
one additional constructor:
\texttt{MessageFifo(const char *prefix, const char *name, int size = 16)}
which is used when a MessageFifo is instantiated outside an \texttt{sc\_module},
where the hierarchical prefix to the name must be provided explicitly by
the user.

\section{Function sendMsg}

A high-level function which takes an endpoint name and a message and does the
name lookup and the write together.


\end{document}
